---
title: "Mapping with more data"
author: "Haoyu Wang"
date: "11/10/2020"
output:
  revealjs::revealjs_presentation:
    theme: solarized
    highlight: pygments
    css: leaflet-reveal.css
    center: FALSE
    transition: slide
---
```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
library(readr)
library(tidyverse)
library(magrittr)
library(lubridate)
library(readr)
library(tidyverse)
library(leaflet)
library(usmap)
library(rgdal)
library(maps)
library(geojsonio)
library(tigris)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

## Introduction
<font size ="5">
<p align="left">
In this assignment, I tried to use the dataset named Public Assistance Funded Projects Details from FEMA for mapping practice. The Public Assistance Funded Projects Details dataset contains obligated (financial obligation to grantee) Public Assistance projects, lists public assistance recipients designated as applicants in the data, and a list of every funded, individual project, called project worksheets. Open projects still under pre-obligation processing are not represented.
Here is the link for data: 
https://www.fema.gov/openfema-data-page/public-assistance-funded-projects-details-v1
</p >
</font>

## Data Clean
<font size ="5"> <p align="left">
I took each county of hurricane data from 2009-2018 for visualization. Moreover, I want to show the mean obligated amount in my map, thus I grouped each county and calculated the mean of total obligated. Since the original csv file is too large, after cleaning, I made a new csv file storing the data I will ues for mapping. In my new dataset, each county has only one value of obligated number, which is the mean of thoes ten years. Here is the preview of my new dataset:
</p >
</font>

```{r, echo = FALSE, message = FALSE, warning = FALSE}
PublicAssistanceFundedProjectsDetails <- read_csv("PublicAssistanceFundedProjectsDetails.csv")
PAF <- PublicAssistanceFundedProjectsDetails
PAF_hurricane <- PAF %>% filter(incidentType == "Hurricane")
PAF_hurricane$declarationDate %<>% year()
PAF_hurricane %<>% filter(declarationDate >2008 & declarationDate < 2019 )
PAF_hurricane$stateNumberCode %<>% formatC(width = 2, flag = 0)
PAF_hurricane$countyCode %<>% formatC(width = 3, flag = 0)
PAF_hurricane %<>% mutate(fips = str_c(stateNumberCode, countyCode))
PAF_hurricane %<>% select(-c(3, 4, 5, 6, 8, 9, 10, 12, 14, 15, 16, 17, 20, 21, 22))
PAF_hurricane$obligatedDate %<>% round_date(unit = 'year')
PAF_hurricane$fips %<>% as.character()
PAF_hurricane %<>% .[-which(.$county == "Statewide"), ]
PAF_hurricane %<>% select(-3)
temp <- group_by(PAF_hurricane, fips)
display <- summarise(temp, state = unique(state),
                     Amount = mean(totalObligated))

display %<>% rename(GEO_ID = fips)
write.csv(PAF_hurricane, file = "PAF_hurricane.csv", row.names = F)
kable(head(PAF_hurricane),"html") %>%
  kable_styling(font_size = 15)
```

## Mapping using leaflet
```{r}
xy <- geojsonio::geojson_read("gz_2010_us_050_00_5m.json", what = "sp")


xy$GEO_ID %<>% substr(start = 10, stop = 14)

leafmap <- geo_join(xy, display, by = "GEO_ID", how = "inner")

pal <- colorNumeric(palette = "RdPu", domain = leafmap$Amount)

Encoding( x = leafmap$NAME ) <- "UTF-8"

leafmap$NAME <-iconv( x =leafmap$NAME, from = "UTF-8", to = "UTF-8", sub = "" )


popup <- paste0("CountyID: ", leafmap$GEO_ID, "<br>", 
                "County: ", as.character(leafmap$NAME), "<br>", 
                "Mean obligated amount: ", round(leafmap$Amount, 2))

leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>%
  addProviderTiles(providers$Stamen.TonerLines,
                   options = providerTileOptions(opacity = 0.75)) %>%
  setView(-89.275673, 37.098, zoom = 4) %>%
  addPolygons(data = leafmap, 
              fillColor = ~pal(Amount), 
              color = "#BDBDC3",
              fillOpacity = 1, 
              weight = 1, 
              smoothFactor = 0.2,
              popup = popup) %>%
  addLegend(pal = pal, 
            values = leafmap$Amount, 
            position = "bottomright", 
            title = "Mean obligated amount") 
```

